Evaluation of +S2 sea ice forecast and some other better title

### 2025-03-07 analysis/paper/access-ice.qmd
Tidy things up

```{r setup, include=FALSE, cache = FALSE}
library(lubridate)
library(ggplot2)
library(data.table)
library(metR)
library(rcdo)
library(tagger)

@@

```{r extent-delta-compute, fig.height=11.99/cm, fig.width=24.09/cm}
dif_hindcast <- hindcast_extent |> 
  copy() |> 
  _[order(time)] |> 
  _[, dif := c(NA, diff(aice)/diff(as.numeric(as.Date(time)))), by = .(model, forecast_time, member)] |> 
  _[, median_ci(dif), by = .(model, time = update(time, year = 2000))]

@@

```{r}
clim_std2 <- clim_std[errors, on = .NATURAL] |> 
  _[, let(climatology = NULL,
          value = climatology)] |> 
  na.omit() |> 
  _[, version := "climatology"]
```

@@

```{r}
topo_lonlat <- rcdo::cdo_topo(grid = "r360x180") |>
  rcdo::cdo_execute(options = c("-f nc")) |>
  metR::ReadNetCDF(c(z = "topo"), subset = list(lat = c(-90, -60))) |> 
  ggperiodic::periodic(lon = c(0, 360))

topo_lonlat <- here::here("data/raw/ETOPO.nc") |> 
  ReadNetCDF() |> 
  na.omit() 
```

@@

```{r}
t_test <- function(x, y, ...) {

>>>>

```{r setup, include=FALSE, cache = FALSE}
library(lubridate)
library(ggplot2)
library(data.table)
library(metR)
library(rcdo)
library(tagger)
library(patchwork)

@@

```{r extent-delta-compute}
dif_hindcast <- hindcast_extent |> 
  copy() |> 
  _[order(time)] |> 
  _[, dif := c(NA, diff(aice)/diff(as.numeric(as.Date(time)))), by = .(model, forecast_time, member)] |> 
  _[, median_ci(dif), by = .(model, time = update(time, year = 2000))]

@@

```{r clim_std2}
clim_std2 <- clim_std[errors, on = .NATURAL] |> 
  _[, let(climatology = NULL,
          value = climatology)] |> 
  na.omit() |> 
  _[, version := "climatology"]
```

@@

```{r topo_lonlat}
topo_lonlat <- here::here("data/raw/ETOPO.nc") |> 
  ReadNetCDF() |> 
  na.omit() 
```

@@

```{r t_test}
t_test <- function(x, y, ...) {
